Denoising and Covariance Estimation of Cryo-EM Images

### 2017-02-10 echo_talk.tex
Mah dist slide echo talk

\section{Work in Progress}
\begin{frame}<beamer>
\setbeamercovered{transparent}
\frametitle{Current and Future Work}
\begin{itemize}[<+->]
 \item Better class averages
 \item Covariance matrix: Orthogonal Replacement using Kam's method
 \item 3D reconstruction from denoised images, without class averaging
\end{itemize}
\end{frame}

\begin{frame}<beamer>
\setbeamercovered{transparent}
\frametitle{Resources}
\begin{itemize}
 \item Code: \url{https://github.com/PrincetonUniversity/cwf_denoise}
 \item Paper: Journal of Structural Biology: \url{10.1016/j.jsb.2016.04.013}
\end{itemize}
\end{frame}

\begin{frame}<beamer>
\setbeamercovered{transparent}
\frametitle{Acknowledgement}
\begin{itemize}
 \item  NIGMS, AFOSR, Simons
Foundation, Moore Foundation Data-Driven Discovery Investigator Award
\item  Maofu Liao, Sjors Scheres, Irina Serysheva and Joachim Frank
\item Yoel Shkolniskly, Fred Sigworth, Zhizhen Zhao, Joakim And\'en
\end{itemize}
\end{frame}
\end{document}

>>>>

\section{Applications and Extensions}
\begin{frame}<beamer>
\setbeamercovered{transparent}
\frametitle{Applications}
\begin{itemize}[<+->]
 \item Better class averages
 \item 3D reconstruction from denoised images, without class averaging
\end{itemize}
\end{frame}

\begin{frame}<beamer>
\setbeamercovered{transparent}
\frametitle{Better 2D classification}
\begin{itemize}[<+->]
 \item Mahalanobis distance pipeline figure from paper
\end{itemize}
\end{frame}

\end{document}
